Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-16 Manuscript/proof_outline.tex
use same product notation everywhere

\begin{minted}[highlightlines={1}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
def cylinder
    (s : Finset ι) (S : Set (∀ i : s, α i)) :
    Set ((i : ι) → α i) :=
  (fun f : (i : ι) → α i => fun i : s => f i) ⁻¹' S
\end{minted}

@@

\begin{minted}[highlightlines={1}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
def cylinders : Set (Set ((i : ι) → α i)) :=
  ⋃ (s) (S) (_ : MeasurableSet S), {cylinder s S}
\end{minted}

Membership of that set is characterized as follows:
\begin{minted}[highlightlines={1}, framesep = 0pt, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
theorem mem_cylinders
    (t : Set ((i : ι) → α i)) :
    t ∈ cylinders α ↔
      ∃ (s S : _) (_ : MeasurableSet S), t = cylinder s S
\end{minted}
\noindent
The finite set \leanline{s} of the potential coordinates where
the cylinder deviates from the whole set needs not be unique.
From the exists-statement of \leanline{mem_cylinders}, we however choose an
arbitrary such \leanline{Finset ι}, called \leanlinecolor{cylinders.finset}.

@@

def Measure.subset_pi
    (P : ∀ i, Measure (α i)) (I : Finset ι) :
    Measure ((i : I) → (α i)) :=
  Measure.pi (fun (i : I) => (P (i : ι)))
\end{minted}

>>>>

\begin{minted}[highlightlines={1}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
def cylinder
    (s : Finset ι) (S : Set (∀ i : s, α i)) :
    Set (∀ i : ι, α i) :=
  (fun (f : ∀ j : ι, α j) => fun i : s => f i) ⁻¹' S
\end{minted}

@@

\begin{minted}[highlightlines={1}, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
def cylinders : Set (Set (∀ i : ι, α i)) :=
  ⋃ (s) (S) (_ : MeasurableSet S), {cylinder s S}
\end{minted}

Membership of that set is characterized as follows:
\begin{minted}[highlightlines={1}, framesep = 0pt, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
theorem mem_cylinders
    (t : Set (∀ i : ι, α i)) :
    t ∈ cylinders α ↔
      ∃ (s S : _) (_ : MeasurableSet S), t = cylinder s S
\end{minted}
\noindent
The finite set \leanline{s} of the potential coordinates where
the cylinder deviates from the whole set needs not be unique.
From the exists-statement of \leanline{mem_cylinders}, we however choose an
arbitrary such \leanline{Finset ι}, called \leanlinecolor{cylinders.finset}.

@@

def Measure.subset_pi
    (P : ∀ i, Measure (α i)) (I : Finset ι) :
    Measure (∀ i : I, α i) :=
  Measure.pi (fun (i : I) => (P (i : ι)))
\end{minted}
